Scalar and Representative Observables, and Their Associated Statistical Model, for Polarimetric SAR Data

### 2014-03-13 paper_dev/article.tex
Prof Vun's changes, ready for submission?

\begin{abstract}
%Problem statement  
This paper proposes novel scalar and representative observables, including several statistically consistent discrimination measures, which should be useful in the interpretation and processing of multi-dimensional POLSAR data.
% This paper proposes a scalar and representative observable for multi-dimensional POLSAR data,
%  from which statistically consistent discrimination measures can be derived.
%What actually were done? and As the result, what is learned?
Specifically, the statistical behaviour of the POLSAR covariance matrix determinant is used
  to derive a scalar and generic statistical model for multi-dimensional POLSAR data,
  which is shown applicable to the two and three dimensional versions of partial and full monostatic polarimetric SAR data.
As the POLSAR covariance matrix determinant generalizes the SAR intensity towards multiple dimensions,
  the proposed model is able to subsume the traditional SAR intensity model under the umbrella of a unified model. 
%What are the larger implications of the findings presented in this paper?
Consequently, the main beneficial implications of the proposed approach are that
  it provides a consistent theory unifying the currently disconnected proposals for SAR and POLSAR discrimination measures,
  and it simplifies the adaptation of existing SAR data processing techniques for POLSAR data.
%  it enables the adaptation of many existing SAR data processing techniques for POLSAR data,
%  and at the same time, it provides a consistent theory unifying the seemingly disparate discrimination measure proposals for SAR and POLSAR data.
\end{abstract}

@@

%What is the situation, the background context of your research? the BIG problem!
Relentless growth in computing power has allowed the once computationally-demanding Synthetic Aperture Radar (SAR) to become now a feasible and preferred technique for earth observation.
The basic SAR technology has also been extended in a few directions, one of which is polarimetric SAR (POLSAR).
POLSAR exploits the natural polarization property of Electro-Magnetic (EM) waves,
   encoded in multiple channels, compared to traditional one-channel SAR.
%During the past decades, exponential growth in computing power has allowed the once computationally-demanding Synthetic Aperture Radar (SAR)
%technology to become a feasible and preferred technique for earth observation applications.
%SAR technology has since been extended in a few directions, one of which is polarimetric SAR (POLSAR).
%POLSAR extends SAR by exploiting the natural polarization property of Electro-Magnetic (EM) waves,
%  leading to the availability of multi-channel POLSAR data, compared to traditional one-channel SAR data.

%Research Motivation: Why it is important to solve this problem?
%The POLSAR data, however, is multidimensional and stochastic.
POLSAR data, like SAR, is stochastic.
Moreover it is also multi-dimensional, making it even harder to interpret.
It is therefore necessary to establish a simple and intuitive understanding of the data.
%Like SAR data, POLSAR data is stochastic.
%Moreover, it is multi-dimensional, making it even harder to interpret.
%Under this context, it is therefore important to establish a simple and intuitive understanding of the data.
Statistical models are undoubtedly crucial in understanding its stochastic nature.
While several models have been proposed for POLSAR data, they tend to be complex and unintuitive due to the multidimensional nature of the data.
%  unfortunately tend to be complex and not very intuitive due to the multidimensional nature of the data.
Practical POLSAR data processing however, makes heavy use of scalar discrimination measures,
  which should be based on statistically consistent (or signal-independent) models. %for scalar and representative observables of the multidimensional data.
It is thus important to establish scalar and representative observables for multi-dimensional POLSAR data.

>>>>

\begin{abstract}
%Problem statement  
This paper proposes novel scalar and representative observables, including several statistically consistent discrimination measures,
  that would be useful in the interpretation and processing of multi-dimensional POLSAR data.
%What actually were done? and As the result, what is learned?
Specifically, the statistical behaviour of the POLSAR covariance matrix determinant is used
  to derive a scalar and generic statistical model for multi-dimensional POLSAR data,
  which is shown applicable to the two and three dimensional versions of partial and full monostatic polarimetric SAR data.
In addition, the proposed model is also able to subsume the traditional SAR intensity model under the umbrella of a unified model,
  where the SAR intensity is shown to be a one dimension version of the multi-dimensional data.
%As the POLSAR covariance matrix determinant generalizes the SAR intensity towards multiple dimensions,
%  the proposed model is able to subsume the traditional SAR intensity model under the umbrella of a unified model. 
%What are the larger implications of the findings presented in this paper?
Consequently, the main beneficial implications of the proposed approach are that
  it provides a consistent theory unifying the currently disconnected proposals for SAR and POLSAR discrimination measures,
  and it simplifies the adaptation of existing SAR data processing techniques for POLSAR data.
%  it enables the adaptation of many existing SAR data processing techniques for POLSAR data,
%  and at the same time, it provides a consistent theory unifying the seemingly disparate discrimination measure proposals for SAR and POLSAR data.
\end{abstract}

@@

%What is the situation, the background context of your research? the BIG problem!
Relentless growth in computing power has allowed the once computationally-demanding Synthetic Aperture Radar (SAR) to now become a feasible and preferred technique for earth observation.
The basic SAR technology has also been extended in a few directions, one of which is polarimetric SAR (POLSAR).
POLSAR exploits the natural polarization property of Electro-Magnetic (EM) waves,
   encoded in multiple channels, compared to traditional one-channel SAR.
%During the past decades, exponential growth in computing power has allowed the once computationally-demanding Synthetic Aperture Radar (SAR)
%technology to become a feasible and preferred technique for earth observation applications.
%SAR technology has since been extended in a few directions, one of which is polarimetric SAR (POLSAR).
%POLSAR extends SAR by exploiting the natural polarization property of Electro-Magnetic (EM) waves,
%  leading to the availability of multi-channel POLSAR data, compared to traditional one-channel SAR data.

%Research Motivation: Why it is important to solve this problem?
%The POLSAR data, however, is multidimensional and stochastic.
%POLSAR data, like SAR, is stochastic.
%Moreover it is also multi-dimensional, making it even harder to interpret.
%It is therefore necessary to establish a simple and intuitive understanding of the data.
%Like SAR data, POLSAR data is stochastic.
%Moreover, it is multi-dimensional, making it even harder to interpret.
%Under this context, it is therefore important to establish a simple and intuitive understanding of the data.
%Statistical models are undoubtedly crucial in understanding its stochastic nature.
While several models have been proposed for POLSAR data, they tend to be complex and unintuitive due to the multidimensional and stochastic nature of the data.
It is therefore necessary to establish a simple and intuitive model for the 
understanding of the data, and statistical models are undoubtedly suitable due to its stochastic nature.
Furthermore, practical POLSAR data processing also makes heavy use of scalar discrimination measures,
  which should be based on statistically consistent (i.e. signal-independent) models. %for scalar and representative observables of the multidimensional data.
It is thus important to establish scalar and representative observables for multi-dimensional POLSAR data.
